---
title: "Analyses for SESMO Paper"
author: "Andres Baeza"
date: "February 22, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###This document describes the construction and results of statistical models and results of the Agent-based model.

load packages
```{r}
require(ggplot2)
require(RColorBrewer)
require(grid)
require(maptools)
require(sp) 
require(rgdal) # requires sp, will use proj.4 if installed
require(plyr)
require(foreign)
require(ggmap)
require(gridExtra)
require(ggpubr)
require(pscl)
require(coefplot2)
require(glmmADMB)
require(bbmle)
```

#The different statistical models



The models represent changes in the frequency of ponding events in Mexico City.  The statistical regression models presented recreates the large-scale patterns, and the relationship between ponding and infrastructure conditions, garbage, subsidence, runoff, and rainfall.

##Models tested:
Poisson
QuasiPoisson
Zero-Inflated quasipoisson
Negative Binomial
Zero-Inflated Negative Binomial (\ZINB)
```{r}
studyArea_CVG<-readShapeSpatial("C:/Users/abaezaca/Dropbox (Personal)/Layers/sesmo/agebs_abm")
studyArea_CVG@data$estado<-as.factor(substring(studyArea_CVG@data$cvgeo,1,2))
studyArea_CVG@data$municipio<-as.factor(substring(studyArea_CVG@data$cvgeo,3,5))


studyArea_CVG@data$encharca<-round(studyArea_CVG@data$encharca)
studyArea_CVG@data$BASURA<-studyArea_CVG@data$BASURA/1000
studyArea_CVG@data$capac_d<-studyArea_CVG@data$capac_d/1000000
studyArea_CVG@data$escurri<-studyArea_CVG@data$escurri/1000

#test the collinearity
mctest(studyArea_CVG@data[,c(8,9,10,16,17)],y = studyArea_CVG@data$encharca)

#overall test
omcdiag(studyArea_CVG@data[,c(8,9,10,16,17)],y = studyArea_CVG@data$encharca)

#individual variables
imcdiag(studyArea_CVG@data[,c(8,9,10,16,17)],y = studyArea_CVG@data$encharca)

#Fitting
#model 1
glm_ponds_zip<-zeroinfl(encharca~antiguedad+subsidenci+PR_2014+escurri+BASURA, data=studyArea_CVG@data)
summary(glm_ponds_zip)

#model 2
glm_ponds_qp<-glm(formula = encharca~antiguedad+subsidenci+PR_2014+escurri+BASURA,data =studyArea_CVG@data ,family = quasipoisson)
summary(glm_ponds_qp)

#model 1
fit_poiss <- glmmadmb(encharca~antiguedad+subsidenci+PR_2014+escurri+BASURA,data =studyArea_CVG@data,zeroInflation=FALSE, family="poisson")
summary(fit_poiss)

#model 2
fit_zipoiss <- glmmadmb(encharca~antiguedad+subsidenci+PR_2014+escurri+BASURA,data =studyArea_CVG@data,zeroInflation=TRUE, family="poisson")
summary(fit_zipoiss)
 
#model 3
fit_nbinom<- glmmadmb(encharca~antiguedad+subsidenci+PR_2014+escurri+BASURA,data =studyArea_CVG@data,zeroInflation=FALSE, family="nbinom1")
summary(fit_nbinom)

#model 4
fit_zinbinom <- glmmadmb(encharca~antiguedad+subsidenci+PR_2014+escurri+BASURA,data =studyArea_CVG@data,zeroInflation=TRUE, family="nbinom1")
summary(fit_zinbinom)


#Akaike information criteria
AICtab(fit_zipoiss,fit_poiss,fit_nbinom,fit_zinbinom)

#variables names of coefficients
vn <- c("Age","subsidence","Rainfall","runoff","garbage") 
 
#coefficient values plot 
tiff(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SESMO/coefficients_estimate.tiff",width = 16,height = 8,res = 300,units = "cm")

coefplot2(list(P=fit_poiss,
               ZIP=fit_zipoiss,
               NB=fit_nbinom,
               ZINB=fit_zinbinom),
varnames=vn,
legend=TRUE)

dev.off() 

coefplot2(list(P=fit_poiss,
               ZIP=fit_zipoiss,
               NB=fit_nbinom,
               ZINB=fit_zinbinom),
varnames=vn,
legend=TRUE)
 #predictions

#zero-inflated
 p <- predict(glm_ponds_zip, type = "zero")
lambda <- predict(glm_ponds_zip, type = "count")

#Poisson
lambda_s2 <- predict(glm_ponds_qp,type="response")


#model in the future without actions
studyArea_CVG@data$antiguedad=studyArea_CVG@data$antiguedad + 40

p_s1 <- predict(glm_ponds_zip,newdata=studyArea_CVG@data, type = "zero")
lambda_s1 <- predict(glm_ponds_zip,newdata=studyArea_CVG@data, type = "count")



#add predictions to map
studyArea_CVG@data$p_E<-ifelse(rbinom(n=length(p), size = 1, prob = p) > 0, 0, rpois(n=length(lambda), lambda = lambda))
studyArea_CVG@data$p_E_s1<-ifelse(rbinom(n=length(p_s1), size = 1, prob = p_s1) > 0, 0, rpois(n=length(lambda_s1), lambda = lambda_s1))

studyArea_CVG@data$p_E_s2<-predict(glm_ponds_qp,type="response")
studyArea_CVG@data$p_E_s2b<-predict(glm_ponds_qp,newdata=studyArea_CVG@data,type="response")

#zero-inflated neg-bin
studyArea_CVG@data$p_E_ZINB<-predict(fit_zinbinom,type='response')
studyArea_CVG@data$p_E_ZINB_b<-predict(fit_zinbinom,newdata=studyArea_CVG@data,type='response', na.action = na.exclude)

```


```{r}

#create breaks based on quantiles of ponding
#brk=c(0,quantile(studyArea_CVG@data$NewPond[which(studyArea_CVG@data$NewPond>0)]))
brk=c(-1,1,5,10,15,20,100)
brk_age=c(-1,20,40,60,80,200)
#bkr=c(0,20,50,100,200,800)
studyArea_CVG@data<-transform(studyArea_CVG@data, z.M=cut(studyArea_CVG@data$p_E, breaks=brk))

studyArea_CVG@data<-transform(studyArea_CVG@data, z.M_s1=cut(studyArea_CVG@data$p_E_s1, breaks=brk))
studyArea_CVG@data<-transform(studyArea_CVG@data, z.M_s2=cut(studyArea_CVG@data$p_E_s2, breaks=brk))
studyArea_CVG@data<-transform(studyArea_CVG@data, z.M_s2b=cut(studyArea_CVG@data$p_E_s2b, breaks=brk))
studyArea_CVG@data<-transform(studyArea_CVG@data, z.M_ZINB=cut(studyArea_CVG@data$p_E_ZINB, breaks=brk))
studyArea_CVG@data<-transform(studyArea_CVG@data, z.M_ZINB_b=cut(studyArea_CVG@data$p_E_ZINB_b, breaks=brk))

studyArea_CVG@data<-transform(studyArea_CVG@data, z.D=cut(studyArea_CVG@data$encharca, breaks=brk))


colors1 <- colorRampPalette(c("lightyellow","lightgreen","green","lightblue","blue","grey"))(length(levels(studyArea_CVG@data$z.D)))
color2<-rev(colorRamps::blue2yellow(6))
colors4 <- colorRampPalette(c( "lightyellow","yellow","orange","red","darkred"))(length(levels(studyArea_CVG@data$z.D)))

studyArea_CVG@data$id =rownames(studyArea_CVG@data)
  studyArea_CVG.points = fortify(studyArea_CVG, region="id")
  studyArea_CVG.df = join(studyArea_CVG.points, studyArea_CVG@data, by="id")

  
  
 M_model<-ggplot(studyArea_CVG.df,
  aes(long,lat,group=group,fill=z.M)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Model",values=setNames(color2, levels(studyArea_CVG@data$z.M)),guide="none")+ggtitle("zero-inflated Poisson")

 M_model_s1<-ggplot(studyArea_CVG.df,
  aes(long,lat,group=group,fill=z.M_s1)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Model_s1",values=setNames(color2, levels(studyArea_CVG@data$z.M_s1)),guide="none")+ggtitle("zero-inflated Poisson (+40 years)") 

 M_model_s2<-ggplot(studyArea_CVG.df,
  aes(long,lat,group=group,fill=z.M_s2)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Model_s2",values=setNames(color2, levels(studyArea_CVG@data$z.M_s2)),guide="none")+ggtitle("Only Poisson") 

  M_model_s2b<-ggplot(studyArea_CVG.df,
  aes(long,lat,group=group,fill=z.M_s2b)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Number of poonding",values=setNames(color2, levels(studyArea_CVG@data$z.M_s2b)),guide="none")+ggtitle("Only Poisson (+40 years)") 
  
  M_model_ZINB<-ggplot(studyArea_CVG.df,
  aes(long,lat,group=group,fill=z.M_ZINB)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Number of poonding",values=setNames(color2, levels(studyArea_CVG@data$z.M_ZINB)))+ggtitle("ZINB") +
    theme(plot.title = element_text(size = 12, face = "bold"))  
  
 M_model_ZINB_b<-ggplot(studyArea_CVG.df,
  aes(long,lat,group=group,fill=z.M_ZINB_b)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Number of poonding",values=setNames(color2, levels(studyArea_CVG@data$z.M_ZINB_b)))+ggtitle("ZINB + 40")+
    theme(plot.title = element_text(size = 12, face = "bold"))  
  
  
  M_model_ZINB_continuous<-ggplot(studyArea_CVG.df,
  aes(long,lat,group=group,fill=p_E_ZINB)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
    ggtitle("ZINB") +
    theme(plot.title = element_text(size = 12, face = "bold"))+
scale_fill_gradient(low = color2[1],high = color2[5])  

  
 
  
   M_data<-ggplot(studyArea_CVG.df,aes(long,lat,group=group,fill=z.D)) +
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Data",values=setNames(color2,levels(studyArea_CVG@data$z.D)))+ggtitle("Ponding (mean events 2004-2014)")+
    theme(plot.title = element_text(size = 12, face = "bold"))  
  
  
  names<-c("Azcapotzalco","Coyoacán","Cuajimalpa","Gustavo A. Madero","Iztacalco","Iztapalapa","Magdalena Contreras","Milpa Alta","Álvaro Obregón","Tláhuac","Tlalpan","Xochimilco","Benito Juárez","Cuauhtémoc","Miguel Hidalgo","Venustiano Carranza")
ID=c("002","003","004","005","006","007","008","009","010","011","012","013","014","015","016","017")

M_data

grid.arrange(M_model,M_model_s1,M_model_s2,M_model_s2b,M_model_ZINB, M_model_ZINB_b,ncol=2)          
   
tiff(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SESMO/ZINB_regression_model.tiff",width = 12,height = 8,res = 300,units = "cm")

ggarrange(M_model_ZINB, M_model_ZINB_b,ncol=2,common.legend = T)  
dev.off()
```

#read results from ABM spatial simulations.
First, simulation assuming single loop using both preferences from SACMEX (two sets of weights). Then, results from simulating the double coupling.
```{r,fig.width=18,fig.height=10}
studyArea_CVG@data$Age_Fin_FN<-numeric(length(studyArea_CVG@data$AGEB_ID))
studyArea_CVG@data$Age_Fin_FM<-numeric(length(studyArea_CVG@data$AGEB_ID))

studyArea_CVG@data$Age_Fin_SL<-numeric(length(studyArea_CVG@data$AGEB_ID))
studyArea_CVG@data$Age_Fin_DL<-numeric(length(studyArea_CVG@data$AGEB_ID))

studyArea_CVG@data$pond_F_FN<-numeric(length(studyArea_CVG@data$AGEB_ID))
studyArea_CVG@data$pond_F_FM<-numeric(length(studyArea_CVG@data$AGEB_ID))

studyArea_CVG@data$pond_F_SL<-numeric(length(studyArea_CVG@data$AGEB_ID))
studyArea_CVG@data$pond_F_DL<-numeric(length(studyArea_CVG@data$AGEB_ID))

studyArea_CVG@data$capasidad_final<-numeric(length(studyArea_CVG@data$AGEB_ID))
studyArea_CVG@data$Acts<-numeric(length(studyArea_CVG@data$AGEB_ID))
studyArea_CVG@data$Act_M<-numeric(length(studyArea_CVG@data$AGEB_ID))
studyArea_CVG@data$Act_N<-numeric(length(studyArea_CVG@data$AGEB_ID))

studyArea_CVG@data$Act_M_SL<-numeric(length(studyArea_CVG@data$AGEB_ID))
studyArea_CVG@data$Act_N_SL<-numeric(length(studyArea_CVG@data$AGEB_ID))

studyArea_CVG@data$Act_M_DL<-numeric(length(studyArea_CVG@data$AGEB_ID))
studyArea_CVG@data$Act_N_DL<-numeric(length(studyArea_CVG@data$AGEB_ID))


map_b<-scan(file = 'C:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SHV/FN-1200-1200-0.2-0.1.txt')
map_d<-scan(file = 'C:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SHV/FM-1200-1200-0.2-0.1.txt')

#with double coupling
map_a<-scan(file = 'C:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SHV/DC-1200-1200-0.2-0.1.txt')
map_c<-scan(file = 'C:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SHV/SC-1200-1200-0.2-0.1.txt')


for (i in seq(1,length(map_b),7)){

  studyArea_CVG@data$Age_Fin_FN[which(studyArea_CVG@data$AGEB_ID ==map_b[i])]<-map_b[i+1]
  
studyArea_CVG@data$Age_Fin_FM[which(studyArea_CVG@data$AGEB_ID ==map_d[i])]<-map_d[i+1]

studyArea_CVG@data$Age_Fin_SL[which(studyArea_CVG@data$AGEB_ID ==map_c[i])]<-map_c[i+1]

studyArea_CVG@data$Age_Fin_DL[which(studyArea_CVG@data$AGEB_ID ==map_a[i])]<-map_a[i+1]
 #flooding results

studyArea_CVG@data$pond_F_FN[which(studyArea_CVG@data$AGEB_ID ==map_b[i])]<-map_b[i+2]

studyArea_CVG@data$pond_F_FM[which(studyArea_CVG@data$AGEB_ID ==map_d[i])]<-map_d[i+2]

studyArea_CVG@data$pond_F_SL[which(studyArea_CVG@data$AGEB_ID ==map_c[i])]<-map_c[i+2]
studyArea_CVG@data$pond_F_DL[which(studyArea_CVG@data$AGEB_ID ==map_a[i])]<-map_a[i+2]

#actions
studyArea_CVG@data$Act_N[which(studyArea_CVG@data$AGEB_ID ==map_b[i])]<-  round(map_b[i+5])
studyArea_CVG@data$Act_N_SL[which(studyArea_CVG@data$AGEB_ID ==map_c[i])]<-  round(map_c[i+5])
studyArea_CVG@data$Act_N_DL[which(studyArea_CVG@data$AGEB_ID ==map_a[i])]<-  round(map_a[i+5])

studyArea_CVG@data$Act_M[which(studyArea_CVG@data$AGEB_ID ==map_b[i])]<-  round(map_b[i+6])
studyArea_CVG@data$Act_M_SL[which(studyArea_CVG@data$AGEB_ID ==map_c[i])]<-  round(map_c[i+6])
studyArea_CVG@data$Act_M_DL[which(studyArea_CVG@data$AGEB_ID ==map_a[i])]<-  round(map_a[i+6])

}

#create categorical variables

studyArea_CVG@data<-transform(studyArea_CVG@data, zAB_FN=cut(studyArea_CVG@data$pond_F_FN,breaks=brk))
studyArea_CVG@data<-transform(studyArea_CVG@data, zAB_FM=cut(studyArea_CVG@data$pond_F_FM, breaks=brk))

studyArea_CVG@data<-transform(studyArea_CVG@data, zAB_SL=cut(studyArea_CVG@data$pond_F_SL,breaks=brk))
studyArea_CVG@data<-transform(studyArea_CVG@data, zAB_DL=cut(studyArea_CVG@data$pond_F_DL, breaks=brk))


studyArea_CVG@data<-transform(studyArea_CVG@data, zAB_age_FN=cut(studyArea_CVG@data$Age_Fin_FN,breaks=brk_age))
studyArea_CVG@data<-transform(studyArea_CVG@data, zAB_age_FM=cut(studyArea_CVG@data$Age_Fin_FM,breaks=brk_age))
studyArea_CVG@data<-transform(studyArea_CVG@data, zAB_age_SL=cut(studyArea_CVG@data$Age_Fin_SL,breaks=brk_age))
studyArea_CVG@data<-transform(studyArea_CVG@data, zAB_age_DL=cut(studyArea_CVG@data$Age_Fin_DL,breaks=brk_age))

colors5 <- colorRampPalette(c("white","cadetblue1","cornflowerblue","orange","red","azure4"))(length(levels(studyArea_CVG@data$zAB_age_FN)))


  studyArea_CVG.points = fortify(studyArea_CVG, region="id")
  studyArea_CVG.df = join(studyArea_CVG.points, studyArea_CVG@data, by="id")

  M_modelABM_s4<-ggplot(studyArea_CVG.df,
  aes(long,lat,group=group,fill=zAB_FN)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Model_ABM_s3",values=setNames(color2, levels(studyArea_CVG@data$zAB_FN)),guide="none")+ggtitle("ABM FN-1200-1200-0.2-0.1")
  

  M_modelABM_s6<-ggplot(studyArea_CVG.df,
  aes(long,lat,group=group,fill=zAB_FM)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Model_ABM_s3",values=setNames(color2, levels(studyArea_CVG@data$zAB_FM)),guide="none")+ggtitle("ABM FM-1200-1200-0.2-0.1")
 
   
tiff(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SESMO/models_and_data_map.tiff",width = 16,height = 10,res = 600,units = "cm")

grid.arrange(M_modelABM_s4,M_modelABM_s6,ncol=2)       

dev.off()

grid.arrange(M_modelABM_s4,M_modelABM_s6,ncol=2)          



```

#Investments
```{r}
 M_modelABM_s7<-ggplot(studyArea_CVG.df,
  aes(long,lat,group=group,fill=Act_N)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_gradient(name="Model_ABM_s3",low=colors4[1],high=colors4[5],guide="colourbar")+ggtitle("ABM Investments New FN-1200-1200-0.2-0.1")

M_modelABM_s8<-ggplot(studyArea_CVG.df,
  aes(long,lat,group=group,fill=Act_M)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_gradient(name="Model_ABM_s4",low=colors4[1],high=colors4[5],guide="colourbar")+ggtitle("Investments mant  FN-1200-1200-0.2-0.1")

  ggarrange(M_modelABM_s7,M_modelABM_s8,ncol=2,common.legend = T)
```


#Age
```{r}
  M_modelABM_age_FN<-ggplot(studyArea_CVG.df,aes(long,lat,group=group,fill=zAB_age_FN)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Age",values=setNames(colors5, levels(studyArea_CVG@data$zAB_age_FN)))+ggtitle("ABM Age FN-1200-1200-0.2-0.1")
  

  M_modelABM_age_FM<-ggplot(studyArea_CVG.df, aes(long,lat,group=group,fill=zAB_age_FM)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Age",values=setNames(colors5, levels(studyArea_CVG@data$zAB_age_FM)))+ggtitle("ABM Age FM-1200-1200-0.2-0.1")
  
  
  ggarrange(M_modelABM_age_FN,M_modelABM_age_FM,ncol=2,common.legend = T)
```




Double-loop learning / Double coupling

#time series
```{r, echo=FALSE,fig.height=4,fig.width=10,fig.align="center"}


TS_A<-read.csv(file="C:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SESMO/ABM-Empirical-MexicoCity_V6_SESMO Age_infra.csv",header = T,skip = 16)
TS_P<-read.csv(file="C:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SESMO/ABM-Empirical-MexicoCity_V6_SESMO ponding.csv",header = T,skip = 16)

P_TS_A<-ggplot(data=TS_A,aes(x=x,y=y))+
  geom_path()+
  scale_x_continuous("years")+
  scale_y_continuous("Average Age",limits = c(0,40))+
  geom_vline(xintercept = 20,linetype=2,colour="red")+annotate("text",x=37,y=40,label='a',size=12)

P_TS_P<-ggplot(data=TS_P,aes(x=x,y=y))+
  geom_path()+
  scale_x_continuous("years")+
  scale_y_continuous("Average Ponding",limits = c(0,10))+
  geom_vline(xintercept = 20,linetype=2,colour="red")+annotate("text",x=37,y=10,label='b',size=12)

tiff(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SESMO/timeseries_DoubleCoupling.tiff",width = 16,height = 8,res = 300,units = "cm")
ggarrange(P_TS_A,P_TS_P,ncol=2)
dev.off()
ggarrange(P_TS_A,P_TS_P,ncol=2)
```

#Number of ponding -single and double coupling
```{r, echo=FALSE,fig.height=5,fig.width=10}

 M_modelABM_SL<-ggplot(studyArea_CVG.df,
  aes(long,lat,group=group,fill=zAB_SL)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Model_ABM_SC",values=setNames(color2, levels(studyArea_CVG@data$zAB_SL)),guide="none")+ggtitle("Single coupling")+annotate("text",x=-98.85,y=19.56,label='a',size=12)
  
 M_modelABM_DL<-ggplot(studyArea_CVG.df,
  aes(long,lat,group=group,fill=zAB_DL)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Model_ABM_SC",values=setNames(color2, levels(studyArea_CVG@data$zAB_DL)),guide="none")+ggtitle("Double coupling")+annotate("text",x=-98.85,y=19.56,label='b',size=12)

 tiff(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SESMO/ponding_doubleCoupling.tiff",width = 16,height = 8,res = 300,units = "cm")
ggarrange(M_modelABM_SL ,M_modelABM_DL,ncol=2)

dev.off()
ggarrange(M_modelABM_SL ,M_modelABM_DL,ncol=2)

```

#Age infra single and double coupling 
```{r}
  M_modelABM_age_SL<-ggplot(studyArea_CVG.df,aes(long,lat,group=group,fill=zAB_age_SL)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Age",values=setNames(colors5, levels(studyArea_CVG@data$zAB_age_SL)))+ggtitle("Single coupling")+annotate("text",x=-98.85,y=19.56,label='a',size=12)
  

  M_modelABM_age_DL<-ggplot(studyArea_CVG.df, aes(long,lat,group=group,fill=zAB_age_DL)) + 
  geom_polygon() +
  coord_equal(xlim = c(-99.4, -98.8),ylim = c(19.2, 19.6))+
  scale_fill_manual(name="Age",values=setNames(colors5, levels(studyArea_CVG@data$zAB_age_DL)))+ggtitle("Double coupling")+annotate("text",x=-98.85,y=19.56,label='b',size=12)
  
tiff(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SESMO/age_infraDoubleCoupling.tiff",width = 16,height = 8,res = 300,units = "cm")  
  ggarrange(M_modelABM_age_SL,M_modelABM_age_DL,ncol=2,common.legend = T)
  dev.off()
  ggarrange(M_modelABM_age_SL,M_modelABM_age_DL,ncol=2,common.legend = T)
```



#Number of pondings by Delegation
```{r, echo=FALSE,fig.height=5,fig.width=10}
A<-read.csv(file="C:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SESMO/ABM-Empirical-MexicoCity_V6_SESMO_doublecouppling-table.csv",header = T,skip = 6)

l <- reshape(A, 
  varying = names(A)[11:26],
  v.names = "Flooding",
  timevar = "Delegation", 
  times = names(A)[11:26], 
  direction = "long")
null_s<-numeric(16)
for(i in 1:16){
null_s[i]<-sum(subset(studyArea_CVG@data, municipio== levels(studyArea_CVG@data$municipio)[i])$p_E_s2)
}

names_M<-c("Azcapotzalco","Coyoacán","Cuajimalpa","Gustavo A. Madero","Iztacalco","Iztapalapa","Magdalena Contreras","Milpa Alta","Álvaro Obregón","Tláhuac","Tlalpan","Xochimilco","Benito Juárez","Cuauhtémoc","Miguel Hidalgo","Venustiano Carranza")
ID=c("002","003","004","005","006","007","008","009","010","011","012","013","014","015","016","017")

Null_M=as.data.frame(cbind(names_M,ID,null_s))
Null_M$null_s=as.numeric(as.character(Null_M$null_s))

G1<-ggplot(subset(l,Eficiencia_Mantenimiento==0.2),aes(x=reorder(Delegation,-Flooding, order = T),y=Flooding,colour=switch_MCDA))+
    geom_segment(aes(xend=reorder(Delegation,-Flooding, order = T),y=Flooding,yend=0),colour="grey60",size=.9)+  
  geom_point(size=4) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+

   scale_y_continuous(name = "Flooding [Events / year]",limits = c(0, 2500))+
   scale_color_discrete(name="Relative importance",label=c("Single loop","Double loop"))+
   annotate("rect", xmin=0, xmax=16, ymin=0 , ymax=500, alpha=0.1, fill="green")+
   annotate("rect", xmin=0, xmax=16, ymin=500 , ymax=1500, alpha=0.1,  fill="yellow")+
   annotate("rect", xmin=0, xmax=16, ymin=1500 , ymax=2500, alpha=0.1, fill="red")+
  theme_bw()+
      theme(
         text=element_text(size = 10),
        axis.line.x= element_line(linetype="solid", colour="black"),
        axis.line.y=element_blank(),
        panel.grid.major.y = element_line(colour="grey80",linetype="dashed"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor =element_blank(),
        panel.border=element_blank(),
       # axis.ticks.y=element_blank(),
       # axis.ticks.x=element_blank(),
        legend.box = "vertical",
    legend.box.margin = margin(3, 3, 3, 3), 
    legend.margin = margin(),
    legend.box.background = element_rect(colour = "black"),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=12,hjust=1,vjust=1,colour = "black",angle = 45),
        axis.title.y=element_blank(),
        axis.title.x=element_blank())
tiff(filename = "c:/Users/abaezaca/Dropbox (ASU)/MEGADAPT/SESMO/pondingbyDelegationDoubpleCoupling.tiff",width = 16,height = 10,res = 600,units = "cm")
  G1 
dev.off()
  G1  
```

##Null model
The results from the poisson model without interventions
```{r, echo=FALSE,fig.height=5,fig.width=10}
G2<-ggplot(data=Null_M,aes(x=reorder(names,-null_s, order = T),y=null_s))+
geom_point(colour="black")+
      theme(
         text=element_text(size = 12),
        axis.line.x= element_line(linetype="solid", colour="black"),
        axis.line.y=element_blank(),
        panel.grid.major.y = element_line(colour="grey80",linetype="dashed"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor =element_blank(),
        panel.border=element_blank(),
        axis.ticks.y=element_blank(),
        axis.ticks.x=element_blank(),
        legend.box = "vertical",
    legend.box.margin = margin(3, 3, 3, 3), 
    legend.margin = margin(),
    legend.box.background = element_rect(colour = "black"),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=17,hjust=1,vjust=1,colour = "black",angle = 45),
        axis.title.y=element_blank(),
        axis.title.x=element_blank())
G2
```


#save results in shapefile
```{r}
writeSpatialShape(studyArea_CVG,fn ="agebs_ABM_resultados" )
```
